Enhancement of Speech Recognition Results Using Server-side Post-processing

### 2019-06-30 none_cloud_post_processing_decoding/doc/main.tex
update the paper

\begin{subequations}
  \begin{align}
    \text{On-Device Speech Recognition}   : 
        & \quad \{ \, \cdots ,\, \vec{x}[m],     \cdots \, \} \rightarrow  
                \{ \, \cdots ,\, \hat{z}_o[l],   \cdots \, \} \\
    \text{Server-Side Post-Processing} : 
        & \quad \{ \, \cdots ,\, \hat{z}_o[l],   \cdots \, \}  \rightarrow
                \{ \, \cdots ,\, W_i,   \cdots \, \}
  \end{align}
\end{subequations}
where $\vec{x}[m]$ is the speech feature vector with $m$ being the 
frame index and $\hat{z}_o[l]$ is the frame-synchronous hypothesis 
from the speech recognizer with $l$ being the frame index. More details
about the frame-synchronous hypothesis will be covered in Sec. 
\ref{sec:frame_synchronous_hypothesis}. The reason for using a different
frame index $l$ for $\hat{z}_o[l]$ is that the frame period in hypothesis
generation may be different from the frame period in feature extraction.
As will be discussed in Sec \ref{sec:frame_synchronous_hypothesis}, 
the sequence of $\hat{z}_o[l]$ is a stream of graphemes.

When the server-side post processing is needed, the sequence of

@@

In this section, we describe how to obtain frame-synchronous  
hypothesis from a speech recognition decoder.

@@

The loss function in the frame-synchronous inference case
$\mathbb{L}_{\text{fs}}\left(\mathcal{X}[0:M], \mathcal{Y}_{0:L}\right)$ is 
defined as follows:
\begin{align}
  \mathbb{L}_{\text{fs}}\left(\mathcal{X}[0:M], \mathcal{Z}[0:M]\right) 
      = \sum_{l=0}^{M-1} 
          \sum_{v=0}^{V-1}  
            (\vec{z}[m])_v  
            \log (\widehat{\vec{z}}[m])_v  
        \label{eq:frame_synchronous_ce_loss} 
\end{align}

>>>>

\begin{subequations}
  \begin{align}
    \text{On-Device Speech Recognition}   : 
        & \quad \{ \, \cdots ,\, \vec{x}[m],     \cdots \, \} \rightarrow  
                \{ \, \cdots ,\, \hat{y}_o[l],   \cdots \, \} \\
    \text{Server-Side Post-Processing} : 
        & \quad \{ \, \cdots ,\, \hat{y}_o[l],   \cdots \, \}  \rightarrow
                \{ \, \cdots ,\, W_i,   \cdots \, \}
  \end{align}
\end{subequations}
where $\vec{x}[m]$ is the speech feature vector with $m$ being the 
frame index and $\hat{z}_o[l]$ is the frame-synchronous hypothesis 
from the speech recognizer with $l$ being the frame index. More details
about the frame-synchronous hypothesis will be covered in Sec. 
\ref{sec:frame_synchronous_hypothesis}. The reason for using a different
frame index $l$ for $\hat{y}_o[l]$ is that the frame period in hypothesis
generation may be different from the frame period in feature extraction.
As will be discussed in Sec \ref{sec:frame_synchronous_hypothesis}, 
the sequence of $\hat{y}_o[l]$ is a stream of graphemes.

When the server-side post processing is needed, the sequence of  
of frame synchronous hypothesis

@@

In this section, we describe how to obtain frame-synchronous  
hypothesis from a speech recognition decoder. The function of a speech
recognizer is to map a sequence of acoustic feature vectors into
a sequence of graphemes or words. This transformation may be represented 
by the following equation:
\begin{align}
  \mathcal{T} : \left(\mathbb{R}^d\right)^{*} \rightarrow \mathbb{V}^{*}
	\label{eq:transformation}
\end{align}

@@

The loss function in the frame-synchronous inference case
$\mathbb{L}_{\text{fs}}\left(\vec{x}[0:M], y_{0:L}\right)$ is 
defined as follows:
\begin{align}
  \mathbb{L}_{\text{fs}}\left(\vec{x}[0:M], z[0:M]\right) 
      = \sum_{l=0}^{M-1} 
          \sum_{v=0}^{V-1}  
            (\vec{z}[m])_v  
            \log (\widehat{\vec{z}}[m])_v  
        \label{eq:frame_synchronous_ce_loss} 
\end{align}
